---
title: "PKI Environmental Book"
title-block-banner: "red"
title-block-banner-color: "white"
subtitle: "PRIVILIGED & CONFIDENTIAL"
date: "`r Sys.Date()`"
format: 
  html:
    theme: 
      - default
      - theme.scss
    embed: true
    page-layout: full
    toc: true
    toc-location: left
    grid: 
      margin-width: 200px
      body-width: 1000px
    resources: 
      - "*.js"
      - "*.mp3"
    css: style.css
  docx:
    toc: false
    number-sections: false
    prefer-html: true
    highlight-style: github
    reference-doc: quarto-template.docx    
echo: false
error: false
warning: false
editor: source
---


```{bash, eval=FALSE}
# using Docker with env pre-installed, if not installed, use the following:
python3.11 -m venv env
source ./env/bin/activate
wget https://raw.githubusercontent.com/risktoollib/data/master/requirements.txt
pip install -r requirements.txt
pip install git+https://github.com/QuantimIntelligence/quantimintelligence-dev.git
```

```{r}
# market data
library(reticulate)
reticulate::use_virtualenv("./env") 
```

```{python}
import quantimintelligence as qi
import os
 
u = 'PARKLAND027'
p = '5rbBzCbA'
 
mv = qi.data.MarketView(u, p)
daily = mv.get_daily('#ICEECB4M')
quote = mv.get_quote('#ICEECB4M')
```



```{r, echo=FALSE}
# python environment
# library(reticulate)
# url <- "https://raw.githubusercontent.com/risktoollib/data/master/requirements.txt"
# 
# if ((Sys.info()[["sysname"]] == "Windows") | (Sys.info()[["sysname"]] == "Darwin") ) {
#   if (!reticulate::virtualenv_exists("env")) {
#     destfile <- "requirements.txt"
#     curl::curl_download(url = url, destfile = destfile)
#     reticulate::virtualenv_create(envname = "env",
#                                   requirements = destfile)
#     file.remove(destfile)
#   }
#   reticulate::use_virtualenv("env")
# } else {
#   reticulate::use_virtualenv("/home/env") # unix
# }

# global variables

# R
library(webshot2) # for ms word rendering prefer-html: true
library(tidyverse)
library(RTL)
library(purrr)
library(fontawesome)
art <- fa("fas fa-arrow-right", fill = "blue")
ar <- fa("circle-arrow-right", fill = "blue")
up <- fa("circle-arrow-up", fill = "lightgreen")
dn <- fa("circle-arrow-down", fill = "orange")
on <- fa("circle-check", fill = "lightgreen")
eq <- fa("fas fa-equals", fill = "lightgreen")
ne <- fa("fas fa-not-equal", fill = "red")
```


## Strategic Fit

::: callout-tip
##### Recommendations

1. ..
2. ..
:::

```{r}
qibt::biz_models() +
  annotate(geom = "text", x = 1, y = 1, label = "Internal Expo", size = 4, color = "black") +
  annotate(geom = "text", x = 4, y = 1, label = "AB TIER", size = 4, color = "black") +
  annotate(geom = "text", x = 4, y = 2, label = "RGGI", size = 4, color = "black") +
  annotate(geom = "text", x = 4, y = 3, label = "RNG", size = 4, color = "black") +
  annotate(geom = "text", x = 2, y = 3, label = "WA-CA-QC", size = 4, color = "black") +
  annotate(geom = "text", x = 2, y = 2, label = "LCFS", size = 4, color = "black") +
  annotate(geom = "text", x = 2, y = 1, label = "REC", size = 4, color = "black") +
  annotate(geom = "text", x = 4, y = 4, label = "Voluntary", size = 4, color = "black") + 
  geom_segment(aes(x=2.25, y=2, xend=3, yend=2), arrow = arrow(length=unit(0.5, 'cm'))) + 
  annotate(geom = "text", x = 3, y = 3.3, label = "De-risk first \n grow with governance \n and capabilities", size = 3, lwd=3, fontface = 'italic', color = "black")
```


## Valuation

+ Validate Mark to Market.
+ Ensure the right options models are utilized.
+ Validate the nature and size of internal asset offsets.

::: callout-tip
##### Recommendations

1. Align Profit and Loss reporting and market risk sensitivities reports with a core principle of risk management in a non-linear book: A license to operate only arises when Profit and Loss is fully attributed to risks managed on the desk and verified independently.
2. All contractual commitments should be valued daily and reported in the P&L. The current close-out practice for economic P&L is not consistent with best practices, even when the two said transactions are under ISDA (close out netting is not a substitute for daily valuation).
:::

#### Voluntary Credits



Stale MTM `r ar` Large volume `r ar` low liquidity `r eq` danger zone need broker statements



##### Portfolio Valuation

##### Pricing Models

## Risk Management

+ Assess the complete MTM risk profile across a wide range of market scenario.
+ Segment the risk profile by strategic and non-strategic markets.
+ Enable PKI to assess its desired risk profile in light of current exposure.

::: callout-tip
##### Recommendations

1. Size net limits according to market liquidity. Define a threshold for each market consistent with the desired numbers of days to exit a position in an orderly market.
2. ..
:::

##### Sensitivities Profile

##### Stress Testing

A robust stress testing framework must be able to answer the following questions:

1. How bad can it get? The magnitude of potential losses from current market levels.
2. How fast can it happen? The speed of acceleration of losses in light of desk capabilities in managing risk in a gapping market.
3. How likely are the events? The Probability of occurrence.
4. What is the quality of the risk-reward? The quality of risk deployed based on robust analytics.
5. How does it impact the overall business portfolio? Exposure should to a particular book should sized in a manner is aligned with business strategy and risk appetite.


```{r}
library(purrr)
library(RTL)
# Pricing Inputs
S = 40
X = 40
T2M = 1
r = 0.05
d = 0
b = r - d
sigma = 0.25

tmp = sigma

# Generating the grid of all possible scenarios for Stock Price and Implied Volatility.
price <- expand.grid(
  S = seq(20, 60, 1),
  Time2Maturity = c(0.25, 0.5, 1),
  sigma = round(seq(.01, .5, .01), 2),
  r = r,
  d = d
)
# Pricing the Option
price <- price %>% mutate(
  X = X,
  mtm = 0,
  mtm = purrr::pmap(
    .l = list(type = "call",
              S,
              X,
              T2M = Time2Maturity,
              r,
              b,
              sigma),
    .f = RTL::GBSOption
  )
)  %>%
  dplyr::mutate(mtm = purrr::map(
    mtm,
    .f = function(x)
      x$price
  )) %>%
  dplyr::mutate(mtm = as.numeric(mtm)) %>%
  dplyr::as_tibble()

# Chart
dff <- price %>% dplyr::filter(Time2Maturity == 1)

# Create a heatmap using ggplot2
heatmap <- dff %>% 
  ggplot(aes(x = S, y = sigma)) +
  # Create a raster plot with 'S' on the x-axis, 'sigma' on the y-axis, and 'mtm' for fill
  geom_raster(aes(fill = mtm), interpolate = TRUE) + 
  # Use a gradient color scale with 12 rainbow colors
  scale_fill_gradientn(colours = rainbow(12)) +  
  theme(
    panel.grid.major.x = element_blank(),  # Remove major gridlines on the x-axis
    panel.grid.minor.x = element_blank(),  # Remove minor gridlines on the x-axis
    panel.grid.major.y = element_blank(),  # Remove major gridlines on the y-axis
    panel.grid.minor.y = element_blank(),  # Remove minor gridlines on the y-axis
    panel.background = element_rect(fill = "white")  # Set the background color to white
  ) +
  labs(
    title = "Risk Landscape Example for CCA Call Option",  
    subtitle = "Strike = Spot Price = $40, Time to Maturity = 1 year.", 
    x = "CCA Price",
    y = "Implied Volatility",  
    caption = paste0(
           "\u00A9",
           format(Sys.Date(), "%Y"),
           " Quantim Intelligence.",
           " Reproduction permitted with credits."
         ) 
  ) +
  # Add a blue point at (x = 100, y = 0.15)
  geom_point(aes(x = 40, y = 0.25), colour = "blue") + 
  # Add a text annotation "Current Market" at (x = 100, y = 0.17)
  annotate(
    "text",
    x = 40,
    y = 0.27,
    label = "Current Market", 
    size = 3,
    col = "blue"
  ) +  
    annotate(
    "text",
    x = 25,
    y = 0.1,
    label = "Low Likelyhood", 
    size = 3,
    col = "black"
  ) + 
    annotate(
    "text",
    x = 25,
    y = 0.4,
    label = "High Likelyhood \n Price Down -> Volatility Up", 
    size = 3,
    col = "black"
  ) + 
  theme(plot.title = element_text(hjust = 0.5),
          plot.subtitle = element_text(hjust = 0.5, size = 10, color = "blue"),
          plot.caption = element_text(hjust = 0.5, size = 10, color = "darkgrey"))
heatmap
```


##### Liquidity Risk

explore size of position 

## Risk Neutralization

Model liquidity risk arising from documentation asymmetry between cleared and OTC transactions under ISDA.

::: callout-tip
##### Recommendations

1. ..
2. ..
:::

## Trade Documentation